Influence of Connectivity on Dung Beetle Communities

### 2025-06-20 corridor_docs/eric_ms_thesis/MS_thesis.Rmd
formatting

header-includes:
  - \AtBeginDocument{\let\maketitle\relax} # this removes default title section
  - \usepackage{float} #to keep figure in the location placed instead of end
  - \floatplacement{figure}{H}
  - \usepackage{booktabs}
  - \raggedbottom
  - \usepackage{fancyhdr}
  - \pagestyle{plain}
  - \fancyfoot[C]{\thepage}
  - \fancyhead[L]{}
  - \fancyhead[R]{\small{EEC MS Thesis Draft}}
  - \thispagestyle{fancy}
  - \usepackage{tabu}
  - \usepackage{makecell}
  - \usepackage{pdflscape}
  - \usepackage{longtable}
  - \newcommand{\blandscape}{\begin{landscape}}
  - \newcommand{\elandscape}{\end{landscape}}
  - \setlength\parindent{22pt}
  - \usepackage{indentfirst}
  - \renewenvironment{abstract}{}{} #suppress the abstract
  - \usepackage{setspace}
  - \setcounter{secnumdepth}{0} # removes numbering from sections and subsections
  - \usepackage{sectsty}\allsectionsfont{\raggedright}
  - \usepackage{sectsty}\sectionfont{\centering}{\normalfont} # center # headings
  - \usepackage{sectsty}\subsectionfont{\centering}{\normalfont} # center ## headings
  - \usepackage{sectsty}\subsubsectionfont{\normalfont} # center ## headings
  # - \usepackage{sectsty}\subsubsectionfont{\itshape} # no centering but italic subsu
  # - \usepackage{sectsty}\subsubsectionfont{\centering}{ital} # center ### headings
  # - \usepackage{sectsty}\sectionfont{\centering\color{darkmidnightblue}}

>>>>

header-includes:
  - \AtBeginDocument{\let\maketitle\relax} # this removes default title section
  - \usepackage{float} #to keep figure in the location placed instead of end
  - \floatplacement{figure}{H}
  - \usepackage{booktabs}
  - \raggedbottom
  - \usepackage{fancyhdr}
  - \pagestyle{plain}
  - \fancyfoot[C]{\thepage}
  - \fancyhead[L]{}
  - \fancyhead[R]{\small{EEC MS Thesis Draft}}
  - \thispagestyle{fancy}
  - \usepackage{tabu}
  - \usepackage{makecell}
  - \usepackage{pdflscape}
  - \usepackage{longtable}
  - \newcommand{\blandscape}{\begin{landscape}}
  - \newcommand{\elandscape}{\end{landscape}}
  - \setlength\parindent{22pt}
  - \usepackage{indentfirst}
  - \renewenvironment{abstract}{}{} #suppress the abstract
  - \usepackage{setspace}
  - \setcounter{secnumdepth}{0} # removes numbering from sections and subsections
  - \usepackage{sectsty}\allsectionsfont{\raggedright}
  - \usepackage{sectsty}\sectionfont{\centering}{\normalfont} # center # headings
  - \usepackage{sectsty}\subsectionfont{\centering}{\normalfont} # center ## headings
  - \usepackage{sectsty}\subsubsectionfont{\bfseries} # center ## headings
  # - \usepackage{sectsty}\subsubsectionfont{\itshape} # no centering but italic subsu
  # - \usepackage{sectsty}\subsubsectionfont{\centering}{ital} # center ### headings
  # - \usepackage{sectsty}\sectionfont{\centering\color{darkmidnightblue}}
